---
title: "Anonymization"
author: "Joshua Olawoyin OLADIMEJI"
date: "2023-08-10"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Set working directory and load necessary libraries
#```{r}
setwd("C:/Users/user/Documents/RGUMasters/Second Semester/Project/Anonymisation of network traffic data/R Project/Anonymization")

install.packages("stringr")
library(stringr)
install.packages("entropy")
library(entropy)
install.packages("dplyr")
library(dplyr)
```
# PREFIX-PRESERVING CONDENSATION-BASED ANONYMIZATION TECHNIQUE
```{r}
PersonalLatest <- read.csv("~/RGUMasters/Second Semester/Project/Anonymisation of network traffic data/R Project/Anonymization/PersonalLatest.csv", stringsAsFactors=TRUE) # load the dataset

View(PersonalLatest) # view the dataset
```

# Function to anonymize the IP address, split the IP address into octets, and apply prefix-preserving condensation-based
```{r}
anonymize_ip <- function(ip_address, prefix_lenght) 
  {
 octets <- str_split(ip_address, "\\.")[[1]] 
 anonymized_ip <- paste0(octets[1:prefix_length], collapse = ".")
 return(anonymized_ip)
}
anonymize_network_traffic <- function(traffic_data, prefix_length) {
anonymized_data <- sapply(traffic_data, anonymize_ip, prefix_length = prefix_length) 
return(anonymized_data)
}
```

# Sample network traffic dataset with a column named "source" and define the number of octets to keep for the anonymized IP.

```{r}
network_traffic_data <- c("74.125.175.39" , "212.1.144.238" , "192.168.1.145" , "8.8.8.8" , "4.2.2.2" , "40.99.214.130" , "172.217.169.10" , "142.250.187.238" ,"40.99.150.130" , "212.1.144.204" )

prefix_length <- 2 # number of octets to keep
```
# Anonymize using prefix-preserving condensation and display the anonymized data
```{r}
anonymized_traffic_data <- sapply(network_traffic_data, anonymize_ip, prefix_length <- 2)

 print(anonymized_traffic_data)
```
Evaluate accuracy

#Function to calculate Jaccard similarity index
```{r}
calculate_jaccard_similarity <- function(original_data, anonymized_data ) {
 set_original <- unique(sort(original_data)) 
 set_anonymized <- unique(sort(anonymized_data))
intersection <- length(intersect(set_original, set_anonymized))
union <- length(union(set_original, set_anonymized))

jaccard_similarity <- intersection / union
  return(jaccard_similarity)

}
```

# Sample data (original and anonymized)
```{r}
original_data <- c("74.125.175.39" , "212.1.144.238" , "192.168.1.145" , "8.8.8.8" , "4.2.2.2" , "40.99.214.130" , "172.217.169.10" , "142.250.187.238" ,"40.99.150.130" , "212.1.144.204" )

anonymized_data <- c("74.125" , "212.1" , "192.168" , "8.8" , "4.2" , "40.99" , "172.217" , "142.250" ,"40.99" , "212.1" )
```

# Calculate Jaccard similarity index and print the result
```{r}
jaccard_index <- calculate_jaccard_similarity(original_data, anonymized_data)

print(jaccard_index)
cat("jaccard similarity index:", jaccard_index, "\n")
```
Evaluate privacy level (Entropy)
#Function to calculate the entropy of the dataset
```{r}
calculate_entropy <- function(data) {
  num_elements <- length(data)
  if (num_elements == 0) {
    return(0)
  } 
   probabilities <- table(data) / num_elements
  entropy <- -sum(probabilities * log2(probabilities))
  return(entropy)
}
```
# Sample the data (Original and Anonymized)
```{r}
original_data <- c("74.125.175.39" , "212.1.144.238" , "192.168.1.145" , "8.8.8.8" , "4.2.2.2" , "40.99.214.130" , "172.217.169.10" , "142.250.187.238" ,"40.99.150.130" , "212.1.144.204")
anonymized_data <- c("74.125" , "212.1" , "192.168" , "8.8" , "4.2" , "40.99" , "172.217" , "142.250" ,"40.99" , "212.1" )
```

# Calculate the entropy level and print the result
```{r}
entropy_anonymized <- calculate_entropy(anonymized_data)

cat("Entropy of anonymized data:", entropy_anonymized, "\n")
```
Evaluate the injection attack resistance
# Sample original network traffic data (Source) and anonymized data
```{r}
original_data <- c("74.125.175" , "212.1.144" , "192.168.1" , "8.8.8" , "4.2.2" , "40.99.214" , "172.217.169" , "142.250.187" ,"40.99.150" , "212.1.144")

anonymized_data <- c("74.125" , "212.1" , "192.168" , "8.8" , "4.2" , "40.99" , "172.217" , "142.250" ,"40.99" , "212.1"  )
```
# Function to simulate an injection attack and test resistance
```{r}
test_injection_attack_resistance <- function(original_data, anonymized_data, injected_prefix) {
  
if (injected_prefix %in% anonymized_data) {
  cat("Injection Attack: The injected prefix is already present in the anonymized data.\n")
} else {
  modified_anonymized_data <- c(anonymized_data, injected_prefix)
    cat("Injection Attack: The injected prefix is not present in the anonymized data.\n")
    cat("Anonymized Data after Injection:", modified_anonymized_data, "\n")
    {}
}
}
```
# Simulate an injection attack by trying to inject prefix "H" into the anonymized data
```{r}
test_injection_attack_resistance(original_data, anonymized_data, "H")
```
Evaluate false positive
# Generate sample data
```{r}
set.seed(123)
n <-100
condition_present <- rbinom(n, 1, 0.2)
data <- data.frame(
  original_target = condition_present,
  anonymized_target = rbinom(n, 1, 0.5) 
)
```
# Calculate false positive and print the result
```{r}
false_positives <- data$anonymized_target == 1 & data$original_target == 0
false_positive_count <- sum(false_positives)
false_positive_rate <- false_positive_count / sum(data$original_target == 0)

cat("False Positive Count:", false_positive_count, "\n")
cat("False Positive Rate:", false_positive_rate, "\n")
```





# CONDENSATION-BASED DIFFERENTIAL ANONYMIZATION TECHNIQUE

```{r}
anonymize_ip_differential <- function (ip_address) {
  octets <- str_split(ip_address, "\\.") [[1]]
  anonymized_octets <- sapply(octets, function(octet) {
    as.integer(octet) %% 10 # Replace each octet with its module 10 value
  }
    )
  anonymize_ip <- paste0(anonymized_octets, collapse = ".")
  return(anonymize_ip)
}
```
# Anonymize the network traffic data using condensation-based differential

```{r}
anonymize_network_traffic_differential <- function(traffic_data) {
  anonymized_data <- sapply(traffic_data, anonymize_ip_differential)
  return(anonymized_ip)
}

anonymize_network_traffic_differential <- function(traffic_data) {
  anonymized_data <- sapply(traffic_data, anonymize_ip_differential)
  return(anonymized_data)
}
```
# Sample network traffic data with destination IP addresses

```{r}
network_traffic_data <- c("192.168.1.145" , "212.1.144.238" , "74.125.175.39" , "212.1.144.204" )
```
# Anonymize the data and print the results

```{r}
anonymized_traffic_data <- anonymize_network_traffic_differential(network_traffic_data)

print(anonymized_traffic_data)
```
# Measure the entropy level of the anonymized data.
```{r}
calculate_entropy <- function(data) {
   data <- as.factor(data)
   prob_dist <- prop.table(table(data))
   entropy_value <- entropy(prob_dist)
     return(entropy_value)
}
```
# Sample anonymized data 

```{r}
anonymized_data <- c("2.8.1.5", "2.1.4.8", "4.5.5.9", "2.1.4.4" )
```
# Measure the entropy level of the anonymized data and print the results

```{r}
entropy_value <- calculate_entropy(anonymized_data)
print(paste("Entropy:", entropy_value))
```
Evaluate using Jaccard Similarity Index (Accuracy)


#Sample original network traffic data and anonymized network traffic data
```{r}
original_data <- c( "192.168.1.145" , "212.1.144.238" , "74.125.175.39" , "212.1.144.204")

anonymized_data <- c("2.8.1.5", "2.1.4.8", "4.5.5.9", "2.1.4.4" )
```

# Function to calculate Jaccard similarity index

```{r}
calculate_jaccard_similarity <- function(original_data, anonymized_data) {
  intersection <- length(intersect(original_data, anonymized_data))
  union <- length(union(original_data, anonymized_data))
  jaccard_similarity <- intersection / union
  return(jaccard_similarity)
}
```
# Calculate the Jaccard similarity index

```{r}
jaccard_similarity_index <- calculate_jaccard_similarity(original_data, anonymized_data)
```
# Display the Jaccard similarity index
```{r}
cat("Jaccard Similarity Index:", jaccard_similarity_index, "\n")
```
Evaluate the injection attack resistance on condensation-based differential
# Sample original and anonymized network traffic data (Destination)

```{r}
original_data <- c("192.168.1" , "212.1.144" , "74.125.175" , "212.1.144" )

anonymized_data <- c("2.8.1", "2.1.4", "4.5.5", "2.1.4")
```

# Function to simulate an injection attack and test resistance

```{r}
test_injection_attack_resistance <- function(original_data, anonymized_data, injected_prefix) {

if (injected_prefix %in% anonymized_data) {
  cat("Injection Attack: The injected prefix is already present in the anonymized data.\n")
} else {
  modified_anonymized_data <- c(anonymized_data, injected_prefix)
    cat("Injection Attack: The injected prefix is not present in the anonymized data.\n")
    cat("Anonymized Data after Injection:", modified_anonymized_data, "\n")
  {}
}
}
```

# Simulate an injection attack by trying to inject prefix "Z" into the anonymized data

```{r}
test_injection_attack_resistance(original_data, anonymized_data, "Z")
```


Evaluate False positive
#Generate sample data
```{r}
n <- 100  # Number of data points
condition_present <- rbinom(n, 1, 0.2)  # Assuming a 20% presence of the condition
data <- data.frame(
  original_target = condition_present,
  anonymized_target = rbinom(n, 1, 0.5)  # Simulating anonymized target data with 50% presence
)
```
# Evaluate false positive

```{r}
false_positives <- data$anonymized_target == 1 & data$original_target == 0
false_positive_count <- sum(false_positives)
false_positive_rate <- false_positive_count / sum(data$original_target == 0)
```

# Print the results
```{r}
cat("False Positive Count:", false_positive_count, "\n")
cat("False Positive Rate:", false_positive_rate, "\n")
```


